Introduction of using AWS instance to run experiments

### 2022-04-05 docs/run_experiments.Rmd
Update docs

```
1, 2, 4, 5 -> 1, 2, 5 -> 1, 2 -> 1
                      -> 2, 5 -> 2
                              -> 5
2, 3, 4, 5 -> 2, 3, 4 -> 2, 3 -> 3
                      -> 2, 4 -> 4
```

@@

Steps in production:

@@

python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3'

aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1

rm -rf results/prediction
```

```{r}
# Get imgs in S3
library(aws.s3)
library(dplyr)
library(parallel)
items <- get_bucket(bucket = "activemapper", 
                    prefix = "leisong/predict", 
                    max = Inf)
keys <- unlist(lapply(c(2: length(items)), function(i) {
    gsub("leisong/", "", items[[i]]$Key)
}))

catalog_pred <- read.csv("results/tanzania/dl_catalog_predict.csv", 
                         stringsAsFactors = FALSE)
fns <- catalog_pred$img %>% unique()

fns <- setdiff(fns, keys)
pth_from <- '/Volumes/elephant'
pth_to <- 's3://activemapper/leisong'
mclapply(fns, function(tile_pth) {
    print(tile_pth)
    cmd <- sprintf('aws s3 cp %s/%s %s/%s',
                   pth_from, tile_pth, pth_to, tile_pth)
    system(cmd, intern = TRUE)
}, mc.cores = 10)
```

@@

#### Post-cleaning

>>>>

```
1, 2, 4, 5 -> 1, 2, 5 -> 1
                      -> 2
                      -> 5
2, 3, 4, 5 -> 2, 3, 4 -> 3
                      -> 4
```

@@

`tools/parse_img_from_s3.R` is a script to grab image stacks from S3 to local machine.

Steps in production (for records):

```
# Grab models, it could be more specific because prediction just uses 2 final models
aws s3 cp --recursive s3://activemapper/leisong/model $HOME/hrlcm/results/dl

# Navigate to hrlcm
cd ~/hrlcm

# Run all steps for different zones together 
Rscript tools/parse_img_from_s3.R -z 1 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 1 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone1_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone1;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 2;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone2;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 5;python hrlcm/predict.py --args_path 'results/dl/unet_z125_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z125_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone5.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone5;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 3;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone3.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone3;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 1;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_1.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/tanzania/predict;Rscript tools/parse_img_from_s3.R -z 4 -s 2;python hrlcm/predict.py --args_path 'results/dl/unet_z234_ft_80epochs/checkpoints/args.pkl' --checkpoint_file 'results/dl/unet_z234_ft_80epochs/checkpoints/final.pth' --fname_predict 'dl_catalog_predict_zone4_2.csv' --data_dir 'results/tanzania' --out_dir 'results/prediction' --stats_dir 'results/tanzania/norm_stats' --num_workers 48 --batch_size 32 --gpu_devices '0,1,2,3';aws s3 cp --recursive $HOME/hrlcm/results/prediction s3://activemapper/leisong/prediction/zone4;rm -rf results/prediction;rm -rf results/tanzania/predict

@@

@@

#### Post-cleaning (TBD)
